Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-13 eswc-2012/phdsymp.tex
reorg benchmark sota
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@94 43ef1190-90fd-4dd7-a769-d0121f02b80e

Query federation with SPARQL has attracted much attention
from industry and academia alike, and four implementations of basic
query federation were submitted to the SPARQL 1.1 Working Group as
input for the forthcoming
work\footnote{http://www.w3.org/2009/sparql/wiki/Feature:BasicFederatedQuery}. 
The basic query federation feature was
supported by a large number of group members, and the Last Call working
draft of the proposed standard was published on 17~November~2011.

@@

\paragraph{In Benchmarking}

The problems addressed by these studies are almost orthogonal to the
problems considered by my proposed project. While I have heard of some
cases where a hypothesis test is used to demonstrate that one
implementation is better than another, it is seemingly not common
practice. Furthermore, I have not to date seen any work towards using
contemporary statistical methods to evaluate the performance of
software, but I shall admit that my literature study have been limited
to RDF/OWL databases, and practical benchmarks of databases, file
systems, scientific software, etc. Thus, the existence of relevant
references in the deeper computer science literature is a key issue I
would appreciate discussing at the Symposium.

>>>>

Query federation with SPARQL, which is a standardized query language
for the Semantic Web, has attracted much attention
from industry and academia alike, and four implementations of basic
query federation were submitted to the SPARQL 1.1 Working Group as
input for the forthcoming
work\footnote{http://www.w3.org/2009/sparql/wiki/Feature:BasicFederatedQuery}. 
The basic query federation feature was
supported by a large number of group members, and the Last Call working
draft of the proposed standard was published on 17~November~2011.

@@

The problems addressed by existing benchmarks such as the one quoted
above are almost orthogonal to the problems considered by my proposed
project. While I have heard of some cases where a hypothesis test is
used to demonstrate that one implementation is better than another, it
is seemingly not common practice. Furthermore, I have not to date seen
any work towards using contemporary statistical methods to evaluate
the performance of software, but I shall admit that my literature
study have been limited to RDF/OWL databases, and practical benchmarks
of databases, file systems, scientific software, etc. Thus, the
existence of relevant references in the deeper computer science
literature is a key issue I would appreciate discussing at the
Symposium.
